Notes on Perturbational Quantities

### 2011-06-15 docs/pert_notes/pert.tex
add species_pred_type = 2 version

\subsection{Advective force for interface prediction}
In predicting the interface states, we work with an advection-like
equation, and call anything other than the advective term a ``force''.
For example, for a scalar $\phi$, obeying a conservation law with a source term, $f$:
\begin{equation}
\frac{\partial \phi}{\partial t} = -\nabla \cdot (\phi \Ub) + f
\end{equation}
We write this in advective form as:
\begin{equation}
\frac{\partial \phi}{\partial t} = -\Ub \cdot \nabla \phi \, \underbrace{- \phi \nabla \cdot \Ub + f}_{\text{``advective force''}}
\end{equation}
Here we identify the non-advection portion of the divergence of the
flux together with the original force, $f$, as the ``force'' for the
advective equation.  In predicting the interface states, this advective
force will be used in computing the interface states.

@@

>>>>

\subsection{Advective force for interface prediction}
In predicting the interface states, we work with an advection-like
equation, and call anything other than the advective term a ``force''.
For example, for a scalar $\phi$, obeying a conservation law with a source term, $f$:
\begin{equation}
\frac{\partial \phi}{\partial t} = -\nabla \cdot (\phi \Ub) + f
\end{equation}
We write this in advective form as:
\begin{equation}
\frac{\partial \phi}{\partial t} = -\Ub \cdot \nabla \phi \, \underbrace{- \phi \nabla \cdot \Ub}_{\text{``advective force''}} + f
\end{equation}
Here we identify the non-advection portion of the divergence of the
flux as the ``advective force'' for the
advective equation.  In predicting the interface states, this advective
force will be used in computing the interface states.  Depending on the
nature of $f$, it may either appear in the prediction as well or be absent
if the process it describes is incorporated by Strang-splitting.

@@

Here we wish to construct $(\rho X_k)_\mathrm{edge}$ by predicting
$(\rho X_k)$ to the edges as a single quantity.  We start with
Eq.~\ref{species equation}:
\begin{equation}
\frac{\partial(\rho X_k)}{\partial t} =
  -\Ub\cdot\nabla(\rho X_k) - \underbrace{\rho X_k \nabla\cdot\Ub}_{``\rho X_k ~\text{force''}} + \rho \omegadot_k \, . \label{species equation labeled}
\end{equation}
The edge state is created by calling {\tt make\_edge\_scal} in {\tt
  density\_advance} with the underbraced term in (\ref{species
  equation labeled}) as the forcing.  This advective force is computed
by {\tt modify\_scal\_force} with {\tt fullform = .true.}.  We do not
consider the $\omegadot_k$ term in the forcing when Strang-splitting.
